---title: "adsir_hw_5"
author: "Jake Greenberg"
date: "4/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(countrycode)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
```

```{r}
# finding coordinates for every country in the world dataset
world <- ne_countries(scale = "medium", returnclass = "sf")
coordinates <- cbind(world, st_coordinates(st_centroid(world$geometry)))
coordinates <- 
  coordinates %>%
  select(name,sovereignt, type, X,Y)
```

# Exercises

**Question 1: Convert the name of a country of choice into five different languages of your choice. Use the world dataset and use countryname. You can also use ‘codelist’ to look at different destinations. (Remove eval=FALSE)**

```{r}
question1 <-
  world %>%
  filter(name == 'Spain')

#Repeat the code down below for 4 other languages.
countryname(question1$name, 'cldr.name.uk')
countryname(question1$name, 'cldr.name.bn')
countryname(question1$name, 'cldr.name.tk')
countryname(question1$name, 'cldr.name.ja')
countryname(question1$name, 'cldr.name.as')
```

**Question 2: Find the ‘region’ name and code for the top 30 countries. Use ‘countrycode’ for this.**

```{r}
question2 <-
  world %>% 
  head(30)

countrycode(question2$name, origin = 'country.name', destination = 'region')
```

**Question 3: Use the guess_field() function to find the closest match of the origin of the adm0_a3 column in the world dataset.**

```{r}
guess_field(world$adm0_a3)
```



**Question 4: Draw a map with 5 countries with different labels using geom_sf, geom_text and countryname (you have complete freedom over what countries you want to do)**

```{r}
canada_plot <-
coordinates[coordinates$name == 'Canada',] %>%
mutate(label = countryname(name, destination = 'cldr.name.uk'))
  
uk_plot <-
coordinates[coordinates$name == 'United Kingdom',] %>%
mutate(label = countryname(name, destination = 'iso3c'))

egypt_plot <-
coordinates[coordinates$name == 'Egypt',] %>%
mutate(label = countryname(name, destination = 'currency'))

france_plot <-
coordinates[coordinates$name == 'France',] %>%
mutate(label = countryname(name, destination = 'cldr.name.uk'))

spain_plot <-
coordinates[coordinates$name == 'Spain',] %>%
mutate(label = countryname(name, destination = 'un.regionsub.name'))

ggplot() + 
  geom_sf(data = canada_plot) +
  geom_sf(data = uk_plot) +
  geom_sf(data = egypt_plot) +
  geom_sf(data = france_plot) +
  geom_sf(data = spain_plot) +
  geom_text(data = canada_plot, aes(X, Y, label=label), size = 5) +
  geom_text(data = uk_plot, aes(X, Y, label=label), size = 5) +
  geom_text(data = egypt_plot, aes(X, Y, label=label), size = 5) +
  geom_text(data = france_plot, aes(X, Y, label=label), size = 5) +
  geom_text(data = spain_plot, aes(X, Y, label=label), size = 5) 
```


**Question 5: Draw a map that has each country named after the continent it belongs to and colored by their continent. Make sure your map looks like an actual map (not grids, not axis, add a title, a caption, etc.)**

```{r warning=FALSE}
continents <-
  mutate(coordinates) %>%
  mutate(continent = countrycode(sovereignt, origin = 'country.name', destination = 'continent')) %>% 
  mutate(continent = as.factor(continent))

ggplot(data = world) +
    geom_sf(aes(color = continent)) + 
    geom_text(data= continents ,aes(X, Y, label = continent),
    color = "black", check_overlap = TRUE) +
    labs(x = NULL, y = NULL, subtitle = "Each Country Colored and Named for Its Continent") +
    ggtitle("World Map with Each Country Named After Its Continent") +
    theme(panel.background = element_blank())
```
